%-------------------------
% Resume in Latex
% Author : Brice Allen
% Website: https://github.com/brice-allen/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{lipsum}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\hypersetup{
    pdftitle={allenBrice-resume.pdf},
    pdfpagemode=FullScreen,
}
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Brice Allen} & Email : \href{mailto:kiewit.dhepj@aleeas.com}{hello@briceallen.com}\\
  \href{http://www.briceallen.com/}{www.briceallen.com} & Mobile : +1-303-551-4544 \\
  \href{https://www.linkedin.com/in/brice-allen/}{Linkedin} & \href{https://gitlab.com/briceallen}{Gitlab} $\mid$ \href{https://github.com/brice-allen}{Github}
 
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Colorado Denver}{Denver, CO}
      {Bachelors in Computer Science;  Dean's list}{2019 --2022}
    \resumeSubheading
      {Community College of Denver}{Denver, CO}
      {Computer Information Systems;  Dean's list}{2017 -- 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Auraria Campus}{Denver, CO}
      {Student Assistant}{August 2017 - December 2019}
      \resumeItemListStart
        \resumeItem{Creative Technologist}
          {
          \begin{itemize}
              \item Integrated technology into the classroom.
              \item Duties include web editing/design, video editing, photography, graphic design,\\ and creating content for digital platforms.
              \item Personally maintained inventory for all maker space materials, tools, and equipment,\\ including hardware and software. 
              \item Provided one-on-one attention to students while maintaining overall focus on the group.
          \end{itemize}}
        \resumeItem{Information Technology}
          {\begin{itemize}
              \item Assisted the Information Technology Department Chair on facility projects.
              \item Assisted Information Technology Department in setting up and maintaining engineering workstation.
              \item Provided technical support of applications.
              \item Responded to helpdesk calls and documented solutions.
              \item Trained users in PC hardware/software and networks.
          \end{itemize}} 
      \resumeItemListEnd

    \resumeSubheading
      {Hospitality Industry}{Various Locations}
      {General Manager | Sommelier | Wine Director}{Jan 2005 - Oct 2017}
      \resumeItemListStart
        \resumeItem{Sommelier | Wine Director}
          {\begin{itemize}
              \item Certified Sommelier \& Advanced candidate
              \item Managed a front-of-house staff ranging from six to eighty employees.  
              \item Requisitioned all materials and supplies needed for front-of-the-house operations. 
              \item Managed multi-million dollar wine inventories.  
          \end{itemize}}
        \resumeItem{General Manager}
          {\begin{itemize}
            \item Managed budget and payroll. 
            \item Led each shift into service, prepared for success. 
            \item Utilized social media to reach marketing goals. 
            \item Implemented custom Point of Sales software. 
            \item Designed and maintained company websites. 
          \end{itemize}}
        \resumeItem{Consultant}
          {Acts as a discreet, private wine buyer for elite clientele across three states.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
\begin{multicol}
  
\end{multicol}
  \resumeSubHeadingListStart
      \resumeSubItem{\href{https://www.ucdenver.io/}{Startled}}
      {Virtual reality-based exposure therapy. }
    \resumeSubItem{\href{www.dailydoses.dev}{Daily Doses}}
      {A medication reminder application. }
    \resumeSubItem{\href{https://csci-4220.herokuapp.com/}{Spotify Recommendation System}}{Exploratory Data Analysis (EDA) and K-Means Clustering}

  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: C++, C, Python, Go, JavaScript, Julia, MASM, Rust}
     \hfill
    
   }
   \item{ \textbf{Technologies}{: Git, Linux/Unix, Docker, Gradle, AWS, Azure, SQL, macOS, Windows, 3D Printing,\\ Virtual Reality, Augmented Reality, Continuous Integration/Delivery}}
   \item{
    \textbf{Tools}{: Visual Studio, VSCode, Jetbrains Suite, Unity, Xcode, Adobe Suite, Android Studio,\\ Proxmark3, Maya, Nvidia Jetson AI, Arduino, Raspberry Pi, Ubiquiti Unifi}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
